Preprocess

### 2025-10-22 src/data.Rmd
Use and rerun for stateless gpt5

---
title: "Preprocess"
date: "`r format(Sys.time(), '%B %d, %Y')`"
author: "Richard Wen <richard.wen@unityhealth.to>"
---

@@

    model_gpt5 =

@@

            "../tmp/healsl_rd1to2_rapid_gpt5_v1.csv",
            col_select = c("rowid", "cause1_icd10", "round")

@@

            round = as.integer(substr(round, 3, 3))

>>>>

---
title: "Preprocess"
date: "`r format(Sys.time(), '%B %d, %Y')`"
author: "Richard Wen <rrwen.dev@gmail.com>"
---

@@

    model_gpt5 = bind_rows(

@@

            "../tmp/healsl_rd1_rapid_gpt5_v2.csv",

@@

            "../tmp/healsl_rd2_rapid_gpt5_v2.csv",
